Project Creditworthiness

### 2021-07-28 Project 3/Assignment/Creditworthiness/Submission - NND.Rmd
Complete Project 3

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Step 1: Business and Data Understanding
●	What decisions needs to be made?
Determining whether customers are creditworthy to give a loan to.

●	What data is needed to inform those decisions?
Outcome: Credit-Application-Result.

●	What kind of model (Continuous, Binary, Non-Binary, Time-Series) do we need to use to help make these decisions?
Binary model.

@@

The final data set has 13 columns
```{r final}
data <- raw
glimpse(data) 
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE)
```

## Step 1: Business and Data Understanding
###	What decisions needs to be made?
Determining whether customers are creditworthy to give a loan to.

###	What data is needed to inform those decisions?
Outcome: Credit-Application-Result.

###	What kind of model (Continuous, Binary, Non-Binary, Time-Series) do we need to use to help make these decisions?
Binary model.

@@

The final data set has 13 columns
```{r final}
raw <- raw %>% mutate(Credit_Application_Result= as.factor(Credit_Application_Result),
                           Account_Balance= as.factor(Account_Balance),
                           Payment_Status_of_Previous_Credit=as.factor(Payment_Status_of_Previous_Credit),
                           Purpose=as.factor(Purpose),
                           Value_Savings_Stocks=as.factor(Value_Savings_Stocks),
                           Length_of_current_employment=as.factor(Length_of_current_employment),
                           No_of_Credits_at_this_Bank=as.factor(No_of_Credits_at_this_Bank))
data <- raw
glimpse(data) 
```
